Code for list reactions for issues of a reposity. Just for a [Yihui's blog post](https://yihui.name/en/2017/10/emoji-stats-of-github-issues/).

# Quick start

## Loading dependencies

```{r message=FALSE}
dependencies <- c("dplyr", "purrr", "httr", "stringr", "jsonlite")

for (pkg in dependencies) {
  if (!require(pkg, character.only = TRUE)) 
    install.packages(pkg, character.only = TRUE)
}

for (file in list.files("R")) {
  cat(file, "\n")
  source(file.path("R", file))
}
```

## Token

As a default, GitHub only allows `60` API calls per hour for anonymous users, and the `GITHUB_PAT` environment variable is used.  I highly recommend to [Create your own pat](https://github.com/settings/tokens/new) and set env `GITHUB_PAT`， for increasing the unauthenticated rate limit to 5000 for OAuth.

```{r, eval=FALSE}
Sys.setenv(GITHUB_PAT = "your_pat")
```

## List reactions

List reactions of an issue and its comment of a given repository:

```{r reactions, cache=TRUE}
# taken the rstudio/rmakrdown for example
reactions <- github_repo_issue_reactions("rstudio/rmarkdown")
```

There are 46 opened issues in `rstudio/ramrkdown`, var `comment_count` indicates the count of comments of an issue

```{r issue_summary}
grouped_reactions <- dplyr::group_by(reactions, issue_number) %>% 
  dplyr::summarise(comment_count = n() - 1L)
grouped_reactions
```

As mentioned in the [blog post](https://yihui.name/en/2017/10/emoji-stats-of-github-issues/), the most upvoted reactions is comment `320504839` of issue `1020`

```{r most_upvoted}
most_upvoted <- dplyr::filter(reactions, `+1` == max(`+1`))
str(most_upvoted)
# we can view the details in the browser
browseURL(most_upvoted$html_url)
```

# Pagination

Requests that return multiple items will be paginated to `30` items by default. 

**Note:** While we set the page size to the maximum `100` for auto pagination, and seek to not overstep your rate limit (5000 request per hour, once the 
GITHUB_PAT is setted as your personal token).

# gh: GitHub API client in R

Unfortunately，the [gh](https://github.com/r-lib/gh) package, a minimalistic GitHub API client in R, came into my eyes just after finish these codes. 

Maybe I'll rewrite my codes rely on gh for the lowlevel stuff later.

# References

- [https://rpubs.com/marbel/19179](https://rpubs.com/marbel/19179)
- The [vignette](https://cran.r-project.org/web/packages/httr/vignettes/api-packages.html) of httr