Code for list reactions for issues of a reposity. Just for a [blog post](https://yihui.name/en/2017/10/emoji-stats-of-github-issues/) from yihui.

# Quick start

## Loading dependencies

```{r message=FALSE}
dependencies <- c("dplyr", "purrr", "httr", "stringr", "jsonlite")

for (pkg in dependencies) {
  if (!require(pkg, character.only = TRUE)) 
    install.packages(pkg, character.only = TRUE)
}

for (file in list.files("R")) {
  cat(file, "\n")
  source(file.path("R", file))
}
```

## Token

 The GITHUB_PAT environment variable is used for personal access token. [Create your own pat](https://github.com/settings/tokens/new) and set env `GITHUB_PAT`， for increasing the unauthenticated rate limit for OAuth.

```{r, eval=FALSE}
Sys.setenv(GITHUB_PAT = "your_pat")
```

## List reactions

List issue reactions and issue comment reactions of a given repository:

```{r}
# taken the yihui's blogdown repository for example
# reactions <- github_repo_issues_reactions("rstudio/blogdown", state = "all")
```


# Pagination

Requests that return multiple items will be paginated to 30 items by default. 

**Note:** While we set the page size to the maximum 100 for auto pagination, and seek to not overstep your rate limit (5000 request per hour, because the 
GITHUB_PAT is setted as token). You probably want to use a custom pattern for traversing large lists.

# gh: GitHub API client in R

Unfortunately，the [gh](https://github.com/r-lib/gh) package, a minimalistic GitHub API client in R, came into my eyes just after finish these codes. 

Maybe I'll rewrite my codes rely on gh for the lowlevel stuff later.

# References

- [https://rpubs.com/marbel/19179](https://rpubs.com/marbel/19179)
- The [vignette](https://cran.r-project.org/web/packages/httr/vignettes/api-packages.html) of httr